% Jason R. Blevins - Curriculum Vitae
%
% Copyright (C) 2004-2010 Jason R. Blevins
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[10pt,letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
% Comment the following line to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
%\usepackage[sc,osf]{mathpazo}

% In practice, I use the following font packages instead of mathpazo.
% beramono provides a nice fixed-width font. xagaramon uses the
% (commercial) Adobe Garamond font.
%\usepackage[scaled=0.75]{beramono}
%\usepackage[osf]{xagaramon}

% Set your name here
\def\name{Xie Xiaolei}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {computer, mobile, information security},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\ttfamily\mdseries\Large}
\subsectionfont{\ttfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
%\renewenvironment{itemize}{
\newenvironment{aperiod}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{1em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.25em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}[t]{0.5\textwidth}
  Phone: +46 70 489 0472 \\
  Email: \href{mailto:xie.xiaolei@gmail.com}{\tt xie.xiaolei@gmail.com} \\
  Address: Kiviksgatan 7C, 21440 Malm\"{o}, Sweden
  Citizenship: Sweden \\
\end{minipage}

% \section*{Objective}
% A master of mathematical physics and Computer Science is looking for a
% Ph.D position in the areas of stochastic processes, random matrix
% theory and extreme value theory.

\section*{Education}
\begin{itemize}
\item Master of Physics, Lund University, Sweden, January 2011 - June
  2014.
  \begin{itemize}
  \item {\it Subject:} Mathematical Physics -- econophysics
  \item My thesis project was a specialization in the area of economical
    physics and focused on the influence that auto-correlations in 
    return series had on the spectral distribution of an empirical
    covariance matrix. It was titled ``Return Models and Covariance
    Matrices'' and was supervised by Prof. Sven \AA berg.
  \end{itemize}

\item M.Sc.(Tech) Computer Science and Engineering, Aalto University,
  Finland, 2005 - 2008.
  \begin{itemize}
  \item {\it Major Subject:} Mobile Computing - Services and Security
  \item {\it Average grade:} 4.17/5.
  \item   Funded by HIIT, I wrote my thesis ``A Mutual authentication
    and Key Agreement Protocol for the UMTS Network''. The algorithm of my
    protocol proposal was based on the Diffie-Hellman Exchange, but had
    significant modifications and extensions so that the mutual
    authentication between the mobile user and the network was delegated
    to the serving instead of the home network. The protocol design
    incorporated puzzle schemes that demanded unbalanced computing
    resources on the two sides to mitigate Denial-of-Service attacks. I
    made C programs to test the puzzle schemes.
  \end{itemize}

\item B.Sc. Computer Science \& Technology, Beijing Institute of
  Technology, 2001- 2005.
  \begin{itemize}
  \item {\it Average grade:} 85.5/100.
  \item {\it Honors:} \textit{Distinguished Graduates of 2005}.
  \end{itemize}
\end{itemize}

\section*{Employment}
Between April 2004 and January 2011 I worked in the software industry
as a software engineer. I designed and implemented software solutions
in C, C++ and Java.

\section*{Skills}
\begin{itemize}
\item {\bf Programming:} Proficient in C/C++, Java, Matlab
\item {\bf Scientific writing:} Latex
\end{itemize}

\section*{Association}
I am a professional member of the {\it Association of Computing Machinery}.

\section*{Referees}
\begin{itemize}
\item Prof. Sven \AA berg. Email:
  \href{mailto:sven.aberg@matfys.lth.se}{\tt
    sven.aberg@matfys.lth.se}. Telephone: +46 46 222 96 33. Mobile:
  +46 70 557 35 69.

\item Prof. Ferdi
  Aryasetiawan. Email: \href{ferdi.aryasetiawan@teorfys.lu.se}{\tt
    ferdi.aryasetiawan@teorfys.lu.se}. Telephone: +46 46 222 90 89.
\end{itemize}

\end{document}
