\documentclass{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage[bookmarks=true]{hyperref}
\usepackage{bookmark}
\usepackage{graphicx}

\newif\ifALL

\ALLtrue

\input{../physics_common}
\title{Performance and Development Review}
\author{Xie Xiaolei}
\date{\today}
\begin{document}
\maketitle

\ifALL
\section{Research Activities Oct. 2014 - Oct. 2015}
\begin{itemize}
\item Co-authored ``Extreme value analysis for the sample
  autocovariance matrices of heavy-tailed multivariate time
  series''. Paper submitted to the ``Extremes''.
\item Went to the {\it Extreme Value Analysis} Conference in Ann Arbor
  in June, 2015.
\end{itemize}

\section{Goals for Research in the comming year}
\begin{itemize}
\item Finish the ongoing paper with Prof. Jeffrey Collamore on
  importance sampling of probabilities of large exceedances by Matrix
  Markov Additive process.
\item Empirical study of the eigenvalues of covariance and correlation
  matrices, using data of Foreigen Exchange Rates and stock prices
  data.
\item I am most excited by the the possibility of explaining patterns
  found in real-world data using our mathematical model.
\end{itemize}

\section{Teaching Activities Oct. 2014 - Oct. 2015}
\begin{itemize}
\item Helped Prof. Jostein Paulsen in teaching the course
  ``Statistical Methods of Non-life Insurance''. Taught the excercise
  sessions.
\item I hope to provide the students with more insight into the course
  material via the exercise sessions.
\item I consult Prof. Paulsen whenever in doubt about solutions to the
  problems or about how to interact with the students.
\item I feel most satisfied when I myself obtain better understanding
  of the mathematics when discussing the problems with Prof. Paulsen
  and with the students.
\end{itemize}

\section{Career}
\begin{itemize}
\item My aspiration is to work in the industry and apply the methods
  and knowledge learned during my Ph.D studies.
\item I hope to have opportunities of working as a summer internship
  in a major investment bank or hedge fund.
\end{itemize}

\section{Development Plan}
Specific Development goals for the next year:
\begin{itemize}
\item ``Introduction to University Pedagogy'', January 25.-29. 2016.
\item ``Responsible Conduct of Research'', February 2. 2016.
\end{itemize}

\bibliographystyle{unsrt}
\bibliography{../thesis/econophysics}
\end{document}
